%-------------------------
% Resume in LaTeX
% Adapted from Sourabh Bajaj's resume template:
% https://github.com/sb2nov/resume
% Tailored for Jean R. Johnsen
%------------------------

\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\evensidemargin}{-0.45in}
\addtolength{\textwidth}{0.9in}
\addtolength{\topmargin}{-0.55in}
\addtolength{\textheight}{1.15in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\definecolor{heading}{HTML}{17324D}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\color{heading}
}{}{0em}{}[\color{heading}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSkill}[2]{
  \item\small{\textbf{#1}: #2 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.1em, itemsep=0.2em, topsep=0.25em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
% CV STARTS HERE
%-------------------------------------------

\begin{document}

%----------HEADING-----------------
\begin{center}
  {\Huge \textbf{Jean R. Johnsen}}\\[4pt]
  {\large Advanced Automation Engineer}\\[6pt]
  Hedehusene, Denmark \textbar{} +45 28 90 58 07 \textbar{}
  \href{mailto:jeanjohnsen@pm.me}{jrj@hojfrekvens.xyz} \textbar{}
  \href{https://cv.hojfrekvens.xyz/}{cv.hojfrekvens.xyz}
\end{center}

%-----------PROFILE-----------------
\section{Profile}
\small
Advanced Automation Engineer with hands-on experience in ABB 800xA, PCS/DCS application work, and software for technical systems where reliability and clarity matter. Builds and tests automation solutions for GMP-regulated pharmaceutical production at NNE, after delivering ABB 800xA solutions at Tipatek and working close to production at Novo Nordisk in Kalundborg. Brings a practical, GMP-aware mindset to complex pharmaceutical automation projects.
\normalsize

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {NNE}{Aug 2026 -- Present}
    {Advanced Automation Engineer}{Kalundborg, Denmark}
    \resumeItemListStart
      \resumeItem{Design, configure, and test PCS/DCS automation applications for GMP-regulated pharmaceutical production.}
      \resumeItem{Deliver robust automation solutions with focus on reliability, structured verification, and clear documentation.}
      \resumeItem{Work cross-functionally close to production to support quality-critical operations.}
    \resumeItemListEnd

  \resumeSubheading
    {Tipatek A/S}{Mar 2025 -- Aug 2026}
    {Junior Automation Engineer}{Odense, Denmark}
    \resumeItemListStart
      \resumeItem{Developed, configured, and tested ABB 800xA automation solutions, including control logic, system configuration, and operator interfaces.}
      \resumeItem{Supported structured verification, troubleshooting, and quality-focused delivery of industrial automation systems.}
    \resumeItemListEnd

  \resumeSubheading
    {Novo Nordisk A/S}{Aug 2022 -- Feb 2025}
    {Process Operator and IT / Automation Projects}{Kalundborg, Denmark}
    \resumeItemListStart
      \resumeItem{Worked in day-to-day operation of process equipment in pharma production, including troubleshooting and repair in a quality-critical environment.}
      \resumeItem{Contributed to PTFE valve analysis and piping optimization with focus on process robustness and maintainability.}
      \resumeItem{Supported automation and IT improvement efforts through testing, practical problem solving, and collaboration close to production.}
    \resumeItemListEnd

  \resumeSubheading
    {Netcompany}{Jan 2021 -- Jun 2022}
    {Freelance Software Architect}{Remote}
    \resumeItemListStart
      \resumeItem{Delivered mobile and web solutions for Danish clients with focus on system design, maintainability, and secure implementation.}
      \resumeItem{Worked across C\#, backend architecture, and technical decision-making for both small and larger customer projects.}
    \resumeItemListEnd

  \resumeSubheading
    {Level 3 Technologies}{Dec 2017 -- Oct 2018}
    {Junior Software Engineer}{Odense, Denmark}
    \resumeItemListStart
      \resumeItem{Built internal modules, scripts, and prototype tooling that improved technical workflows and sped up proof-of-concept work.}
      \resumeItem{Developed a method for comparing cause-and-effect diagrams with real shutdown events, reducing analysis effort and strengthening traceability.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {SIMAC}{Jan 2025 -- Present}
    {Bachelor of Technology in Marine Engineering}{Svendborg, Denmark}
  \resumeSubheading
    {Processkolen}{Aug 2022 -- Jan 2025}
    {EUD - Process and Optimization}{Kalundborg, Denmark}
  \resumeSubheading
    {University of Southern Denmark}{Sep 2016 -- Jan 2020}
    {Bachelor of Science in Computer Science}{Odense, Denmark}
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0in, label={}]
  \resumeSkill{Automation}{ABB 800xA, ABB SattLine, control logic, operator interfaces, system testing, troubleshooting, technical documentation}
  \resumeSkill{Pharma and production}{GMP-aware work close to production, process equipment, LMES, PAS-X, cross-functional collaboration}
  \resumeSkill{Programming}{C\#, Java, Python, Rust}
  \resumeSkill{Tools and languages}{Git, GitLab, Danish, English}
\end{itemize}

%-----------ADDITIONAL EXPERIENCE-----------------
\section{Additional Experience}
\begin{itemize}[leftmargin=0in, label={}]
  \resumeSkill{TV2}{Student Developer and Data Analyst in a broadcasting environment (2016 -- 2017)}
  \resumeSkill{Hauch's Physiske Cabinet}{Web Developer and Guide, combining technical work with communication (2015)}
  \resumeSkill{Adidas \& Team Danmark}{Former elite athlete with national and international 800m competition experience (2017 -- 2020)}
  \resumeSkill{BHS-PL Beton}{Former continental and danish A series cyclist (2022 -- 2025)}
\end{itemize}

%-------------------------------------------
\end{document}
